Approaching institutional matches of river basin systems

### 2022-07-01 docs/papers/01_manuscript/manuscript.tex
fix: fix abbreviations in abstract

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
     Alignment of social-ecological system (SES) structures is an crucial approach to institutional matches, but understanding of its causal links and underlying processes are still weaknesses.
     To fill these knowledge gaps, the Yellow River Basin in China is a valuable case study, because it is one of the most anthropogenically altered large river basins.
     Under different institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different social-ecological system (SES) structures.
     By creating counterfactual against, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
     Furthermore, these heterogeneous effects aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in YRB restoration.
     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion in basins worldwide.
     }  %! Notice input

>>>>

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
     Alignment of social-ecological system (SES) structures is an crucial approach to institutional matches, but understanding of its causal links and underlying processes are still weaknesses.
     To fill these knowledge gaps, the Yellow River Basin (YRB) in China is a valuable case study, because it is one of the most anthropogenically altered large river basins.
     Under different institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
     By creating counterfactual against, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
     Furthermore, these heterogeneous effects aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in YRB restoration.
     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion in basins worldwide.
     }  %! Notice input
